Command line programs from LatticeRepLib

### 2023-02-05 ProgramSummary/ProgramSummary..tex
Descriptions of the command line programs for lattice studies

\DeclareMathOperator{\mr}{\textfrak{P}_i}
\begin{document}                  % DO NOT DELETE THIS LINE
	\singlespacing
	$\mr$

@@

	\newcommand{\ci}[0]{$c_1$}
	\newcommand{\cii}[0]{$c_2$}
	\newcommand{\ciii}[0]{$c_3$}
	\begin{abstract}
	\end{abstract}

@@

	\begin{table}
		\renewcommand{\arraystretch}{1.2}
		\caption{Programs to convert lattice representations}
		\begin{tabular}{l l l p{.7\textwidth}  l}
			\toprule
			Name		&	in	&	out			& Output	\\
			\midrule
			CmdToB4		&	y	&	\BIV{}		&		For each input, 
			it produces the 4 vectors as a,b,c,d as E3 vectors, 
			and also the lengths of each of those vectors.\\[.9pt]
			CmdToC	3	&	y	&	\CIII{	}	&		
			For each input, produces the \CIII{} representation in the form 
			(\#,\#) (\#,\#) (\#,\#), 
			which does not conform to the format for input to other programs.\\[.9pt]
			CmdToCell	&	y	&	
			\parbox[t]{0.07\textwidth}{${	a,b,c,}$ \\ ${\alpha,\beta,\gamma}$}		&		
			Converts to the conventional unit cell representation.\\[.9pt]
			CmdToDC		&	y	&	\DXIII{}		&	Outputs the lengths of the 13 unique vectors describing the Dirichlet cell.\\[.9pt]			
			CmdToG6		&	y	&	\GVI{}		&		Converts the input to \GVI{}\\[.9pt]
			CmdToS6		&	y	&	\SVI{}		&		Converts the input to \SVI{}\\[.9pt]
			Radial		&	y	&	Polar	&
				CSomputes the polar distances in Angstroms 
				from the first input cell. 
				That is {(a,$\alpha$)}, {(b,$\beta$)}, and {(c,$\gamma$)} 
				as coordinates in complex space.\\[.9pt]
			\bottomrule

@@

		\begin{longtable}{l l l p{.2\textwidth} p{.5\textwidth} l}
			\caption{Summary of programs manipulating data}
			\label{processingprogs}\\ %NOTE: that lineskip is necessary to prevent toprule from crashing
			\toprule
			Name		&	in	&	out		&	\begin{parbox}[t]{2cm}{
				command line\\
				param{s}}
			\end{parbox}	& Output	\\
			\midrule
			CmdCmplx	&	NA	&	y		&\hrulefill	&Currently, 
				this just outputs some programmed examples.		\\[.9pt]
			CmdDelone	&	y	&	\SVI{}	&\hrulefill	&Converts input to \SVI{}		\\[.9pt]
			CmdGen		&	NA	&	\GVI{}	&	ngen - number of examples to generate (optional)\\
				{}		&		&			&type		& - lattice type to 
				generate, many options (optional) 
				c,t,h,o,r,h,m,a, 
				cP, cF,cI, tP, tI, hP, hR, oP, oF, oI, oS, mP, mC, mS, aP, 
				numeric Niggli types - 1-44, 
				Delone types - C1,C3,C5,~\dots 
				If no parameters are present, one each of the 44 Niggli types. 
				If only a number is present, that is how many of each of the 44 Niggli types to generate.
				For usage examples, see Table \ref{CMDGENexamples}\\[.9pt]
			CmdLM		&	y	&	y		&	\hrulefill		&		Lattice Matching. 
				The first input cell is used as the reference. 
				Succeeding cells are matched 
				as well as possible to the reference cell.\\[.9pt]
			CmdNiggli	&	y	&	\GVI{}	&\hrulefill	&		
				Produces the Niggli reduced cell for 	each input\\[.9pt]
			CmdPath		&	y	& \SVI{}			&
			no. of points	& If the number of points is 
			not on the command line, the default number 
			to generate is 20.	If there is only one point, 
			then the second point is generated as the 
			Niggli reduced cell. If more than two points are input, 
			each successive pair will
			generate a list of output points; so if
			3 cells are input, the output will be 
			2 times the number of points requested.	\\[.9pt]
			CmdPerturb	&	y	& y			&	n-number of perturbations,

				parts per thousand to perturb			&
				n cells perturbed normal to the input \SVI{} vector
				If a lattice centering (including P) is input,
				the output is in the same centering. Otherwise, the output is in \SVI{}.	\\[.9pt]
			CmdS6Refl	&	y	&	\SVI{}	&\hrulefill	&	For each input, 
				all 24 \SVI{} reflections are produced.\\[.9pt]
			CmdSella	&	y	&	y		&\hrulefill	&
				SELLA produces 2 output: std::out contains the match of
				each of the 24 Delone types; SVG for the Grimmer
				diagram is written to a file with a name such as 
					\verb#SEL__2023-01-07.08_56_42.svg# with date/time stamp.\\
			CmdSort		&	y	&	y		&"C3" or "seq'&	\\[.9pt]
			CmdVolume	&	y	&	mod		&\hrulefill	&		Outputs the unit cell 
				and the volume of each input cell.\\[.9pt]
			MultiMetricDists&y	& mod		&"Y/y"(optional)&	
				Parameter Y/y for maxima style output		\\[.9pt]
			PlotC3		&	y	&	mod		& \hrulefill	& Plot 
				the three \CIII{} coordinates. See Figure~\ref{plotc3}.\\[.9pt]
			SELLA		&	y	&	mod		&\hrulefill	&	
				Outputs the distances from each of the Bravais lattice types 
				(in \svi{}).	\\[.9pt]
			SVD			&	y	&	mod		&\hrulefill	& Outputs the singular value decomposition vectors
				and eigenvalues for the input lattice. This is done in \SVI{}.		\\[.9pt]			
			\bottomrule

@@

	\begin{itemize}
	\item{CmdGen}

@@

	\item SVD

@@

	\begin{samepage}
		{\nopagebreak{
				\textbf{Command line:}\\
				CmdGen 5 33 | CmdSort seq | SVD\\
				; SVD\\
				S6 from input cell   0.000 -31.196   0.000 -71.963 -109.653 -131.880\\
				S6 from input cell   0.000 -23.060   0.000 -77.367 -110.398 -125.599\\
				S6 from input cell   0.000 -28.898   0.000 -54.985 -106.336 -82.229\\
				S6 from input cell   0.000 -56.133   0.000 -103.736 -177.343 -123.204\\
				S6 from input cell   0.000 -10.111   0.000 -50.618 -91.57100 -98.102\\
			}
		}
	\end{samepage}

@@

@@

			Note that five types (O3, M3, M2B, A2, and A3) are not normal 
			crystallographic types. They are boundary types, and they have
			fewer free parameters than the generic type requires. For instance,
			O3 (character: rs0 rs0) has only two free parameters (r and s), whereas
			an ordinary orthorhombic type requires three variables.}
		\includegraphics[width=0.75\textwidth]{DeloneTypesGrid_3}\\
		\label{s6table}		
	\end{table}

@@

	\ack{{\bf Acknowledgements}}

	\ack{{\bf Funding information}}

@@

	%	\bibliography{reduced}
	%	
	%	\bibliographystyle{iucr}

>>>>

\DeclareMathOperator{\mr}{\textfrak{P}_i}
\begin{document}                  % DO NOT DELETE THIS LINE
	\singlespacing

@@

	\newcommand{\ci}[0]{$c_1$}
	\newcommand{\cii}[0]{$c_2$}
	\newcommand{\ciii}[0]{$c_3$}
%	\begin{abstract}
%	\end{abstract}

@@

	\begin{table}
		\renewcommand{\arraystretch}{1.2}
		\caption{Programs to convert lattice representations.
		NOTE: although all can take all of the input types, \BIV{}. \DXIII{}, 
	Polar write output that cannot be used as input.}
		\begin{tabular}{l l l p{.7\textwidth}  l}
			\toprule
			Name		&	in	&	out			& Output	\\
			\midrule
			CmdToB4		&	y	&	\BIV{}		&		For each input, 
			it produces the 4 vectors as a,b,c,d as E3 vectors, 
			and also the lengths of each of those vectors.\\[.9pt]
			CmdToC	3	&	y	&	\CIII{	}	&		
			For each input, produces the \CIII{} representation in the form 
			(\#,\#) (\#,\#) (\#,\#), 
			which does not conform to the format for input to other programs.\\[.9pt]
			CmdToCell	&	y	&	
			\parbox[t]{0.07\textwidth}{${	a,b,c,}$ \\ ${\alpha,\beta,\gamma}$}	&					Converts to the conventional unit cell representation
			If the input is already unit cell parameters, then the output
			will be in the same lattice centering as the input.\\[.9pt]
			CmdToDC		&	y	&	\DXIII{}		&	Outputs the lengths of the 13 unique vectors describing the Dirichlet cell.\\[.9pt]			
			CmdToG6		&	y	&	\GVI{}		&		Converts the input to \GVI{}\\[.9pt]
			CmdToS6		&	y	&	\SVI{}		&		Converts the input to \SVI{}\\[.9pt]
			Radial		&	y	&	Polar	&
				CSomputes the polar distances in Angstroms 
				from the first input cell. 
				That is {(a,$\alpha$)}, {(b,$\beta$)}, and {(c,$\gamma$)} 
				as coordinates in complex space.\\[.9pt]
			\bottomrule

@@

		\begin{longtable}{l l l p{.2\textwidth} p{.5\textwidth} l}
			\caption{Summary of programs manipulating data}
			\label{processingprogs}\\ %NOTE: that lineskip is necessary to prevent toprule from crashing
			\toprule
			Name		&	in	&	out		&	\begin{parbox}[t]{2cm}{
				command line\\
				param{s}}
			\end{parbox}	& Output	\\[.9pt]
			\midrule
			CmdCmplx	&	NA	&	y		&\hrulefill	&Currently, 
				this just outputs some programmed examples.		\\[.9pt]
			CmdDelone	&	y	&	\SVI{}	&\hrulefill	&Converts input to \SVI{}		\\[.9pt]
			CmdDists	&	y	& mod		&\hrulefill	&For on input list of n
			cells, n-1 distances will be output.\\[.9pt]
			CmdGen		&	NA	&	\GVI{}	&	ngen	&- number of examples to generate (optional)\\
				{}		&		&			&type		& - lattice type to 
				generate (optional); many options 
				c,t,h,o,r,h,m,a, 
				cP, cF,cI, tP, tI, hP, hR, oP, oF, oI, oS, mP, mC, mS, aP, 
				numeric Niggli types - 1-44, 
				Delone types - C1,C3,C5,~\dots 
				If no parameters are present, one each of the 44 Niggli types. 
				If only a number is present, that is how many of each of the 44 Niggli types to generate.
				For usage examples, see Table \ref{CMDGENexamples}\\[.9pt]
			CmdLM		&	y	&	y		&	\hrulefill		&		Lattice Matching. 
				The first input cell is used as the reference. 
				Succeeding cells are matched 
				as well as possible to the reference cell.\\[.9pt]
			CmdNiggli	&	y	&	\GVI{}	&\hrulefill	&		
				Produces the Niggli reduced cell for 	each input.\\[.9pt]
			CmdPath		&	y	& \SVI{}			&
			no. of points	& If the number of points is 
			not on the command line, the default number 
			to generate is 20.	If there is only one point, 
			then the second point is generated as the 
			Niggli reduced cell. If more than two points are input, 
			each successive pair will
			generate a list of output points; so if
			3 cells are input, the output will be 
			2 times the number of points requested.	\\[.9pt]
			CmdPerturb	&	y	& y			&	n-number of perturbations,

				parts per thousand to perturb			&
				n cells perturbed normal to the input \SVI{} vector
				If a lattice centering (including P) is input,
				the output is in the same centering. Otherwise, the output is in \SVI{}.	\\[.9pt]
			CmdS6Refl	&	y	&	\SVI{}	&\hrulefill	&	For each input, 
				all 24 \SVI{} reflections are produced.\\[.9pt]
			CmdSella	&	y	&	y		&\hrulefill	&
				SELLA produces 2 output: std::out contains the match of
				each of the 24 Delone types; SVG for the Grimmer
				diagram is written to a file with a name such as 
					\verb#SEL__2023-01-07.08_56_42.svg# with date/time stamp.\\
			CmdSort		&	y	&	y		&"C3" or "seq'&	CmdSort has 2 possible actions. If "seq" is specified
			as the sort type, then in the incoming list of 
			lattices, in each pair, the second one is multipled by the 24 \SVI{} reflections, and the one that
			is closest to the first is chosen for output.\\[.9pt]
			CmdVolume	&	y	&	mod		&\hrulefill	&		Outputs the unit cell 
				and the volume of each input cell.\\[.9pt]
%			MultiMetricDists&y	& mod		&"Y/y"(optional)&	
%				Parameter Y/y for maxima style output		\\[.9pt]
			PlotC3		&	y	&	mod		& \hrulefill	& Plot 
				the three \CIII{} coordinates. See Figure~\ref{plotc3}. The gray lines
				connect successive pairs of points 
				in the input. The output graphics file
				is an SVG file whose name is in the output
				in standard output.\\[.9pt]
			SELLA		&	y	&	mod		&\hrulefill	&	
				Outputs the distances from each of the Bravais lattice types 
				(in \svi{}).	\\[.9pt]
			SVD			&	y	&	mod		&\hrulefill	& Outputs the singular value decomposition vectors
				and eigenvalues for the input lattice. This is done in \SVI{}.		\\[.9pt]			
			\bottomrule

@@

	\begin{itemize}
		  \setlength\itemsep{3em}
	\item{\textbf{CmdGen}}

@@

	\item \textbf{SVD}

@@

	\begin{samepage}
		{\nopagebreak{
				\textbf{Command line:}\\
				CmdGen 5 33 \textbar~ CmdSort seq \textbar~ SVD\\
				; SVD\\
				S6 from input cell   0.000 -31.196   0.000 -71.963 -109.653 -131.880\\
				S6 from input cell   0.000 -23.060   0.000 -77.367 -110.398 -125.599\\
				S6 from input cell   0.000 -28.898   0.000 -54.985 -106.336 -82.229\\
				S6 from input cell   0.000 -56.133   0.000 -103.736 -177.343 -123.204\\
				S6 from input cell   0.000 -10.111   0.000 -50.618 -91.57100 -98.102\\
			}
		}
	\end{samepage}

@@

	\item \textbf{CmdS6Refl}

	CmdS6Refl generates the 24 reflections (see \cite{Andrews2019b})
	of each input lattice. Duplicate outputs of each input are not removed.

	\item \textbf{CmdPath}

	CmdPath outputs points along a line between pairs of lattice.

	The number of points per segment is a commandline parameter.
	If no parameter is input, the default is 20. This is not
	the number of steps; it is the number of points that will be
	output for a segment (pair of input lattices).

\begin{enumerate}
	\item Only a single lattice is input. A second point will
	be generated as the Niggli reduced lattice, and series of points
	will be output between them.

	\item Two lattices are input. Then the points will be
	created between them.

	\item More than two lattices are input. Then each point
	and its succeeding point will generate a segment. Each segment
	will be output as the number of points specified. Note: the
	final point of one segment and the first point of the next
	segment will be duplicates.
\end{enumerate}

	The line between points is calculated in \SVI{}. The other
	likely space would be \GVI{}, but the results seem to be the same.
	As an example, in the case of 3 items input and 5 requested
	output lattices, the output will consist of 10 lines, 5
	for each successive pair of lattices, and the 5th and
	6th points will be the same.\\

	\textbf{Command Line:}\\
	 CmdPath 5 \\
	; Path generator\\
	f 10 10 10 90 90 90 90\\
	end\\

	\textbf{Output:}\\
	; no. of points output is 5\\
	S    0.00000   0.00000   0.00000 -100.00000 -100.00000 -100.00000    1\\
	S    6.25000   6.25000   6.25000 -100.00000 -100.00000 -100.00000    2\\
	S   12.50000  12.50000  12.50000 -100.00000 -100.00000 -100.00000    3\\
	S   18.75000  18.75000  18.75000 -100.00000 -100.00000 -100.00000    4\\
	S   25.00000  25.00000  25.00000 -100.00000 -100.00000 -100.00000    5\\

	\textbf{Command Line:}\\
	 CmdPath 5  \textbar~ CmdToCell\\
	; To Cell\\
	f 10 10 10  90 90 90\\
	end\\

	\textbf{Output:}\\
	; no. of points output is 5\\
	P  10.00000  10.00000  10.00000  90.00000  90.00000  90.00000\\
	P   9.35414   9.35414   9.35414  85.90396  85.90396  85.90396\\
	P   8.66025   8.66025   8.66025  80.40593  80.40593  80.40593\\
	P   7.90569   7.90569   7.90569  72.54240  72.54240  72.54240\\
	P   7.07107   7.07107   7.07107  60.00000  60.00000  60.00000\\

@@

			Note that five types (O3, M3, M2B, A2, and A3) are not normal 
			crystallographic types. They are boundary types, and they have
			fewer free parameters than the generic type requires. For instance,
			O3 (character: \textit{rs0 rs0}) has only two free parameters (r and s), whereas
			an ordinary orthorhombic type requires three variables.}
		\includegraphics[width=0.85\textwidth]{DeloneTypesGrid_3}\\
		\label{s6table}		
	\end{table}

@@

	\ack{\bf Acknowledgements}

	\ack{\bf Funding information}

@@

		\bibliography{reduced}

		\bibliographystyle{iucr}
